\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
replace weird comma

Automatically inducing programs from examples is a long-standing goal
of artificial intelligence. Recent work has successfully used
symbolic search techniques (e.g., Metagol:~\cite{muggleton2015meta},
FlashFill:~\cite{gulwani2011automating}), neural networks trained from
a corpus of examples (e.g., RobustFill:~\cite{devlin2017robustfill}), and hybrids of neural and
symbolic methods (e.g., Neural-guided deductive search~\cite{ngds}, DeepCoder:~\cite{balog2016deepcoder}) to
synthesize programs for task domains such as string transformations,
list processing, and robot navigation and planning. However, all these
approaches -- symbolic, neural and neural-symbolic -- rely upon a
hand-engineered \emph{Domain-Specific Language} (DSL). The DSL is an
inventory of restricted programming primitives, encoding domain-specific
knowledge about the space of programs. In
practice
we often have only a few input/output examples for each
program to be induced, and thus success often hinges on having a good
DSL, by providing a crucial inductive bias for what would otherwise be an
unconstrained search through the space of all computable functions.
Here we ask, to what extent can we dispense with such highly
hand-engineered domain-specific languages?

>>>>

Automatically inducing programs from examples is a long-standing goal
of artificial intelligence. Recent work has successfully used
symbolic search techniques (e.g., Metagol:~\cite{muggleton2015meta},
FlashFill:~\cite{gulwani2011automating}), neural networks trained from
a corpus of examples (e.g., RobustFill:~\cite{devlin2017robustfill}), and hybrids of neural and
symbolic methods (e.g., Neural-guided deductive search~\cite{ngds}, DeepCoder:~\cite{balog2016deepcoder}) to
synthesize programs for task domains such as string transformations,
list processing, and robot navigation and planning. However, all these
approaches -- symbolic, neural and neural-symbolic -- rely upon a
hand-engineered \emph{Domain-Specific Language} (DSL). The DSL is an
inventory of restricted programming primitives, encoding domain-specific
knowledge about the space of programs. In
practice
we often have only a few input/output examples for each
program to be induced, and thus success often hinges on having a good
DSL that provides a crucial inductive bias for what would otherwise be an
unconstrained search through the space of all computable functions.
Here we ask, to what extent can we dispense with such highly
hand-engineered domain-specific languages?
